### 2023-01-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@db3d8784d332f0b18890069a0d14ddb014fae540 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@03fc93283dfacb8a049af58abd945d3e5baa0c09 🚀

where the maximum \emph{a posteriori} (MAP) estimate of \((\mu, \phi)\)
applied to Mangal data from (MacDonald \emph{et al.} 2020) is
\((\mu=0.086, \phi=24.3)\). All simulations were done with 500
independent replicates of unique niche model networks per unique number
of total interactions observed \(n\). All analyses presented here are
done in Julia v1.8 (Bezanson \emph{et al.} 2015) using both
EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville \emph{et al.}
2021) and are hosted on
\href{https://github.com/gottacatchenall/ms_false_negatives/tree/main/src}{Github}).
Note that the empirical data, for the reasons described above, very
likely already contains many false-negatives, we'll revisit this issue
in the final section.

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

AG \& MDC acknowledge the support of the Liber Ero Chair for
Biodiversity conservation and NSERC.

>>>>

where the maximum \emph{a posteriori} (MAP) estimate of \((\mu, \phi)\)
applied to Mangal data from (MacDonald \emph{et al.} 2020) is
\((\mu=0.086, \phi=24.3)\). All simulations were done with 500
independent replicates of unique niche model networks per unique number
of total interactions observed \(n\). All analyses presented here are
done in Julia v1.8 (Bezanson \emph{et al.} 2015) using both
EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville \emph{et al.}
2021) and are hosted on \href{}{Github} (\textbf{link removed for
double-blind review}). Note that the empirical data, for the reasons
described above, very likely already contains many false-negatives,
we'll revisit this issue in the final section.

@@
